---
title: "Image examples"
output: html_notebook
---

The aim of this project is to take some famous images and only 'represent' them through 'age', 'period' and 'cohort' effects.

The specific tasks are: 

* Find way to download some famous images
* Load the images as matrices
* Model the matrices as
    * Age alone
    * Period alone
    * Cohort alone
    * Age:Period
    * Age:Cohort
    * Age^2^
    * Period^2^
    * Cohort^2^
    * etc

# Find images to download 



```{r load_prereq}
pacman::p_load(
  tidyverse, magick
)
```


```{r load_images, eval = F}
download.file(
  "http://dujye7n3e5wjl.cloudfront.net/photographs/1080-tall/time-100-influential-photos-lunch-atop-skyscraper-19.jpg",
  "images/image_01.jpg",
  mode = "wb"
)

```

Other possible images are [here](http://100photos.time.com/)


Now to try to load this as a matrix 

```{r read_images}
image <- magick::image_read("images/image_01.jpg") %>% 
  image_convert(type = "grayscale") %>% # convert to grayscale
  image_scale("250") %>% #rescale to 250 pixels wide
  image_data()

image_mtrx <- image[1, 1:dim(image)[2], 1:dim(image)[3]]

image_mtrx <- apply(image_mtrx, 1, as.integer)


```


Convert matrix to dataframe

```{r convert_to_df}
image_df <- image_mtrx %>% 
  as_data_frame() %>% 
  mutate(y = dim(.)[1]:1) %>% 
  gather(key = "x", value = "value", -y) %>% 
  mutate(x = stringr::str_replace(x, "V", "") %>% as.integer()) 

```

Now let's plot using ggplot2

```{r show_image_as_df}
image_df %>% 
  ggplot(aes(x = x, y = y, fill = value)) + 
  geom_tile()
```


Now let's start to model this data 

```{r compare_models}

mod_specs <- c(
  age = "value ~ year",
  year = "value ~ age", 
  cohort = "value ~ cohort",
  ap = "value ~ age*year",
  ac = "value ~ age*cohort",
  aa = "value ~ poly(age, 2)",
  pp = "value ~ poly(year, 2)",
  cc = "value ~ poly(cohort, 2)"
) %>% enframe(name = "mod_name", value = "params")

```

```{r change_data}

image_df <- image_df %>% 
  rename(age = y, year = x) %>% 
  mutate(age = age %/% 2) %>% # so max age around 100 not 200
  group_by(age, year) %>% 
  summarise(value = mean(value)) %>%
  mutate(cohort = age - year) %>% 
  select(age, year, cohort, value) %>% 
  mutate(value = value / max(value))


```

Now models

```{r run_models}

mods_fitted <- mod_specs %>% 
  mutate(
    model = map(params, function(x) {
      lm(as.formula(x), data = image_df)
      }
    )
  ) %>% 
  mutate(aic = map_dbl(model, AIC)) %>% 
  arrange(aic)


```

Now to calculate the fit surfaces  

```{r calc_model_fits}

get_fitted_values <- function(MDL, DTA){
  out <- broom::augment(MDL, DTA) %>% 
    as_data_frame()
}

mods_fitted <- mods_fitted %>% 
  mutate(fitted_surface = map(model, get_fitted_values, DTA = image_df)) 

```

Now an HAPC 

```{r calc_hapc_model}
image_df %>% 
  ungroup() %>% 
  mutate(value = (value - mean(value)) / sd(value)) %>% 
  lme4::lmer(value ~ age + I(age^2) + (year | cohort), data = .) -> mod_hapc

image_df %>% 
  ungroup() %>% 
  mutate(value = (value - mean(value)) / sd(value)) %>% 
  lme4::lmer(value ~ age + I(age^2) + (1 | cohort), data = .) -> mod_hac

image_df %>% 
  ungroup() %>% 
  mutate(value = (value - mean(value)) / sd(value)) %>% 
  lme4::lmer(value ~ age + I(age^2) + (1 | year), data = .) -> mod_hap


```

```{r show_model_fits }
mods_fitted %>% 
  select(mod_name, fitted_surface) %>% 
  unnest() %>% 
  ggplot(aes(x = year, y = age, fill = .fitted)) + 
  geom_tile() + 
  facet_wrap(~mod_name) +
  scale_fill_gradientn("Fitted Value", colours = scales::brewer_pal(palette = "Paired")(12)) 

```


Now residuals

```{r show_model_resids }
mods_fitted %>% 
  select(mod_name, fitted_surface) %>% 
  unnest() %>% 
  ggplot(aes(x = year, y = age, fill = .resid)) + 
  geom_tile() + 
  facet_wrap(~mod_name) +
  scale_fill_gradientn(
    "Residuals", 
    limits = c(-0.6, 0.6),
    colours = scales::brewer_pal(palette = "RdBu")(5)
  )


```


```{r show_image_itself_multi}
image_df %>% 
  ggplot(aes(x = year, y = age, fill = value)) +
  geom_tile() +
  scale_fill_gradientn("Fitted Value", colours = scales::brewer_pal(palette = "Paired")(12)) 

```

```{r show_image_itself_grey}
image_df %>% 
  ggplot(aes(x = year, y = age, fill = value)) +
  geom_tile() +
  scale_fill_gradient("Fitted Value", low = "white", high = "black") 

```
